---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = '#>',
  fig.path = 'man/figures/README-',
  out.width = '100%'
)
```

# xengagement

<!-- badges: start -->

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-green.svg?style=flat-square)](https://lifecycle.r-lib.org/articles/stages.html#stable)

<!-- badges: end -->

`{xengagement}` is a package that predicts the amount of Twitter engagement that [xGPhilosophy](https://twitter.com/xGPhilosophy) receives with its end-of-match xG summary tweets. The predictions are shared with automated tweets made by [a bot](https://twitter.com/punditratio), occasionally including some manually inserted commentary :grinning:.

Read [this Twitter thread](https://twitter.com/TonyElHabr/status/1373277253572960258?s=20) for a high-level discussion of how the package can be used to gain insights. Also, see [this dashboard](https://xengagement.herokuapp.com/) using outputs from this package. (Yes, that is a python-based web app :snake: using outputs from an R package :laughing:.)

## Installation

You can install the development version of `{xengagement}` from [GitHub](https://github.com/) with:

```{r eval=F}
# install.packages('remotes')
remotes::install_github('tonyelhabr/xengagement')
```

## Developer Usage

-   `data-raw/update.R`: Run the [Twitter bot](https://twitter.com/punditratio).

-   `data-raw/98_train.R`: Re-train models.

-   `data-raw/99_evaluate.R`: Update plots used in [Twitter thread](https://twitter.com/TonyElHabr/status/1373277253572960258?s=20).

-   `data-raw/00_scrape_colors.R`: Re-scrape team colors. The results have to be added manually to the `team_mapping.csv` file. (Not using `{teamcolors}` package since it may or may not be kept up-to-date.)

-   `data-raw/01_generate_team_mapping.R`: Update internal team mapping data sets, presumably when there are changes to EPL teams (e.g. at the beginning of a new season). Also, update team account Twitter followers (which isn't done with `transform_tweets()` to prevent hitting the Twitter API a ton).
