---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = '#>',
  fig.path = 'man/figures/README-',
  out.width = '100%'
)
```

# xengagement

<!-- badges: start -->

[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-experimental-orange.svg?style=flat-square)](https://www.tidyverse.org/lifecycle/#experimental)

<!-- badges: end -->

`{xengagement}` is a package that predicts the amount of Twitter engagement that [xGPhilosophy](https://twitter.com/xGPhilosophy) receives with its end-of-match xG summary tweets. The predictions are shared with automated tweets made by [a bot](https://twitter.com/punditratio), occasionally including some manually inserted commentary :grinning:.

## Installation

You can install the development version of `{xengagement}` from [GitHub](https://github.com/) with:

```{r eval=F}
# install.packages('remotes')
remotes::install_github('tonyelhabr/xengagement')
```
